Creating optimal conditions for reproducible data analysis in R with `fertile`

### 2020-02-19 fertile.Rmd
added citations

bibliography: bibliography.bib
output: rticles::asa_article
---

@@

As Goodman, Fanelli, and Ionnidis argue in their 2016 paper, *What does research reproducibilty mean?*, the language and conceptual framework of research reproducibility vary across the sciences. There are no clear standards agreed upon across fields.

@@

@@

>>>>

bibliography: [bibliography.bib, pkgs.bib]
output: rticles::asa_article
---

```{r, include=FALSE}
knitr::write_bib(c("dplyr", "drake"), file = "pkgs.bib")
```

@@

As @goodman2016does argue, the language and conceptual framework of research reproducibility vary across the sciences. There are no clear standards agreed upon across fields.

@@

Much of the available literature focuses on file structure, organization, and naming, and `fertile`'s features are consistent with this. The *ideal* file structure is not agreed upon by academics, though there are some recommendations focused on R that are available. @marwick2018packaging provides the framework for file structure that `fertile` is based on: a structure similar to that of an R package, with an `R` folder, as well as `data`, `data-raw`, `inst` and `vignettes`.

@@

See also the **drake** package [@R-drake].
